---
title: "Finalizing Results & Moving to Report"
author: "Public Interest Data Lab"
date: "Spring 2019"
output: 
  html_document:
    toc: true
    theme: yeti
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Volumes/PIDL19")

library(tidyverse)
library(stargazer)
library(RColorBrewer)
library(lubridate)


dss <- readRDS("dss.rds")
```


# Figures

First, some code to create a visualization.

```{r}
# from the example_analysis_R.r script!
# Create a data frame to generate a graph ----
# subset data 
# children in foster care; only whte, black, multirace; only removal variables and race
dss_remove <- dss %>% 
  filter(fc_enter == "Yes") %>% 
  filter(race %in% c("White", "Black", "MultiRace")) %>% 
  dplyr::select(race, remove_physabuse:remove_house)

# drop unused race levels, and recode reasons
dss_remove$race <- droplevels(dss_remove$race)
var <- c(names(dss)[100:114])
dss_remove <- dss_remove %>% 
  mutate_at(var, as.numeric) %>% 
  mutate_at(var, list(~ dplyr::recode(., `1` = 0L, `2` = 1L)))

# reshape to long
remove <- dss_remove %>% 
  gather(reason, count, -race) %>% 
  group_by(race, reason) %>% 
  summarize(tot = sum(count))

# add total number of children in each racial category to data frame
remove_race <- dss_remove %>% count(race)
remove <- left_join(remove, remove_race, by = "race")
remove <- remove %>% 
  mutate(prop = tot/n)

# make reason a factor and order by prop
remove <- remove %>% 
  mutate(reason = factor(reason),
         reason = fct_reorder(reason, prop))

# Generate a figure of reasons ---
ggplot(remove, aes(x = reason, y = prop, fill = race)) + 
  geom_col(width=0.9, position=position_dodge(.75)) +
  scale_fill_manual(values = brewer.pal(9, "Oranges")[c(8,6,4)]) +
  coord_flip() +
  labs(title = "Reasons for Removal from Home By Race",
       subtitle = "CPS Removals from January 2, 2015 to December 29, 2017", 
       y = "Proportion of Children Removed for Reason", x = "Reason for Removal")
```

## Steps to Export Visualizations in R
1. Run the code for the visualization the the console (the plot should appear under the plots tab in the lower right quadrant of the screen).
2. Click Export > Save as PDF (*PDF images have the best resolution when embedded in the report*). Give the plot a descriptive name (like "all-removals-prop"), and same the image. 
3. Resize the image to reasonable dimensions. You can either resize the image dimensions by resizing the plot viewer (dragging the sides) or in the export step. Make sure PDF size is set to `(Device Size)` so that it maintains the dimensions of the viewer, or change the width and height dimensions in export.

## Steps to Get a Visualizations into Overleaf

1. Open the Overleaf project and click the upload button in the top left corner (the third icon below the Menu button). Upload the PDF(s) and drag them into the `plots` folder. (*If you click the plots folder before uploading, they will automatically be in the plots folder.*)
2. Now go to the Example Section of the Overleaf doc. See you there!

# Tables 

To make LaTeX tables, we'll be using the `stargazer` package.

First some code from `example_analysis_R.r` to create some example models.

```{r}
# from example_analysis_R.r
# Generate a model for a reason ----
# re-create subsetted data frame for analysis (but keep all vars), recode age
dss_remove <- dss %>% 
  filter(fc_enter == "Yes") %>% 
  filter(race %in% c("White", "Black", "MultiRace")) %>% 
  mutate(age_rem = interval(start = dob, end = remove_currdate) /
           duration(num = 1, units = "years"))

# 1. most basic model: race, age, gender
house1 <- glm(remove_house ~ race + age_rem + gender, 
              data = dss_remove, family = "binomial")

# 2. adding polynomial for age
house2 <- glm(remove_house ~ race + poly(age_rem, 2) + gender, 
              data = dss_remove, family = "binomial")

# 3. adding family structure (reduced to single/two parents)
dss_remove <- dss_remove %>% 
  mutate(care_structure2 = fct_recode(care_structure,
                                      "Single" = "Single mom",
                                      "Single" = "Single dad",
                                      "Dual" = "Married couple",
                                      "Dual" = "Unmarried couple"))
house3 <- glm(remove_house ~ race + age_rem + gender + care_structure2, 
              data = dss_remove, family = "binomial")

# 4. adding numref
house4 <- glm(remove_house ~ race + age_rem + gender + care_structure2 + numref, 
              data = dss_remove, family = "binomial")

# 5. adding ever_find
house5 <- glm(remove_house ~ race + age_rem + gender + care_structure2 + numref + ever_find, 
              data = dss_remove, family = "binomial")
```

Now to making LaTeX tables!

Use the `stargazer` function to get a LaTeX table from your model. Copy and paste the output from begin{table} to end{table} into Overleaf. Meet you there!


```{r}
# run install.packages("stargazer") if you haven't yet
library(stargazer)
stargazer(house1, house2, house3, house4, house5, 
          title="Comparing Logit Regression of Removal Due to Inadequare Housing", 
          covariate.labels=c("Black", "Multiracial", "Age at Removal", 
                             "Polynomial of Age at Removal: 1", 
                             "Polynomial of Age at Removal: 2", "Male", 
                             "Care Structure: Single", "Number of Referrals",
                             "Ever Find L", "Ever Find Q", "Ever Find C"), 
                    type = "latex", star.cutoffs = c(0.25, 0.1, 0.05),
          column.sep.width="1pt", align=TRUE, no.space=TRUE, dep.var.labels.include=FALSE)
# check out ?stargazer to see all the possible arguments
```















